Is the Future of Authenticity All In Our Heads?

### 2017-07-25 paper.tex
Better figures,e tc

% Created 2017-07-14 Fri 10:26
% Intended LaTeX compiler: pdflatex
\documentclass[sigconf]{acmart}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\input{authors}
\setcopyright{rightsretained}
\acmDOI{10.475/123_4}
\acmISBN{123-4567-24-567/08/06}
\acmConference[NSPW '17]{New Security Paradigms Workshop}{October 2017}{Islamorada, Florida, USA}
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}
\date{\today}
\title{Is the Future of Authenticity In Our Heads?\\\medskip
\large Moving Passthoughts From the Lab to the World}
\hypersetup{
 pdfauthor={},
 pdftitle={Is the Future of Authenticity In Our Heads?},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.1.1 (Org mode 9.0.4)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section{Introduction}
\label{sec:orgdac43e4}

@@

\section{Background}
\label{sec:orga960dc5}

@@

\subsection{One-step, multi-factor authentication}
\label{sec:orgd8d138f}

@@

\subsection{Passthought authentication}
\label{sec:org4fb6cdf}

@@

\subsection{Passthoughts using in-ear EEG}
\label{sec:org0297b7e}

@@

\section{User attitudes and perceptions}
\label{sec:org394f76c}

@@

\subsection{Contending with mind-reading machines}
\label{sec:org9ea7d96}

@@

\subsection{What (do you think) EEG can reveal about a person?}
\label{sec:org8834f8e}

@@

This quote highlights how individuals' life experiences
might shape the way they engage (or refuse to engage) with brain-sensing devices.
In general, this quote and others motivate the need for a rich, qualitative understanding of people's first-hand experiences with brainscanning devices,
as well as data collection,
in order to understand what role BCI applications such as passthoughts could play in day-to-day life.
\section{Diversity and security of passthoughts}
\label{sec:orgcbc1766}

@@

\section{Two studies on passthoughts}
\label{sec:org79b0955}

@@

\subsection{A real-time passthought authenticator}
\label{sec:org460629f}

@@

\subsubsection{Study protocol}
\label{sec:org1596012}

@@

\subsubsection{The effect of feedback}
\label{sec:orgd7a13f9}

@@

\subsubsection{Exploring continuous re-calibration}
\label{sec:orgb4e92ba}

@@

\subsection{A longitudinal study on brainwave monitoring}
\label{sec:org212508e}

@@

\subsubsection{Study protocol}
\label{sec:org62d770d}

@@

\subsubsection{A more diverse corpus}
\label{sec:org9e64a25}

@@

\subsubsection{The space of possible passthoughts}
\label{sec:orgf0dd4c4}
In another potentially fruitful analysis, such a corpus will allow us to perform statistical analysis of how passthoughts are drawn from the overall distribution of EEG signals. 
Using multi-dimensional clustering algorithms such as t-SNE \cite{VanDerMaaten2008} 
could assist us in understanding how particular passthoughts relate to other EEG signals that an individual expresses involuntarily throughout the day. 
These clusters will help us understand how likely or unlikely we are to observe a given passthought in context of a particular person's neural signals
Such analysis between subjects could help shed light how given passthoughts are expressed uniquely between individuals.

@@

\subsubsection{Usability and attitudes}
\label{sec:org8c509bd}

@@

\subsubsection{Limitations}
\label{sec:orgaddaf14}

@@

\section{Privacy, Security: Choices, Tradeoffs}
\label{sec:orgbcf3427}

@@

\subsection{Privacy}
\label{sec:org5570c65}
As of yet, it is still not well understood what EEG signals might reveal about a person.
EEG signals that are not anonymized could come to be seen as private in the face of new methods of analysis.
(If your brainwaves can authenticate you, could they also uniquely identify you, even if your name is redacted?)
Differential privacy \cite{Dwork2014} presents one approach to dealing with the risk of privacy breaches with EEG signals.
By adding noise to datasets, differentially private databases can make strong guarantees about the likelihood of a de-anonymization attack on particular database queries.

\subsection{Security}
\label{sec:org3b2d0ae}
Device security presents another risk to passthought authentication.
Since EEG devices will transmit data, likely wirelessly \cite{Mihajlovic2015}, their data may be intercepted, depending on the security properties of the underlying transit protocol. 
When transferring authentication credentials in passthoughts, the ability to snoop on authentication attempts could present a dangerous attack vector.

@@

\subsection{Tradeoffs between security and privacy}
\label{sec:org37085fa}

@@

\section{Further Future Directions}
\label{sec:org7099ddd}

@@

\subsection{Continuous authentication}
\label{sec:orgf2994d6}

@@

\subsection{Organic passwords}
\label{sec:org7858c3a}

If EEG signals are nonstationary (changing over time), passthoughts will require continuous re-calibration to maintain decent accuracy \cite{Vidaurre2006a}.
This feature of BCIs could have an unexpected benefit to security. 
If an individual's expression of their passthought in EEG is always changing, 
passthoughts themselves are effectively evergreen, automatically replaced or updated by nature of the authentication paradigm.
This feature could improve security, as an attacker able to compromise a passthought's EEG signature may not be able to log into the system in a few weeks time,
unless they are able to realistically mutate the signal over authentication attempts.
This feature of EEG also gives passthoughts a possible advantage over other methods for behavioral authentication, such as voice or keystroke dynamics \cite{Monrose1997}, which may change more slowly for individuals, if they change at all.
Future work should investigate this claim, perhaps using a longitudinal corpus such as the one described above.
\subsection{Authentication and the self}
\label{sec:org70dc1bb}

@@

Such a scenario raises serious ethical, legal, and even philosophical questions. 
How does such a system conform to accepted definitions of a ``person''?
Who is a person to make decisions for their future self?
What are possible vectors for abuse?
In any case, this property of an authentication is, as far as we are aware, novel, 
and should be considered as we learn more about the strengths, weaknesses, and particular affordances of this developing method for authentication.
\subsection{Passthoughts by any other sensor?}
\label{sec:orgead9313}

@@

\subsection{Health, neuroscience and BCIs}
\label{sec:org453b8eb}

@@

\section{Conclusion}
\label{sec:orga79be22}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{refs}
\end{document}

>>>>

% Created 2017-07-25 Tue 11:42
% Intended LaTeX compiler: pdflatex
\documentclass[sigconf]{acmart}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\input{authors}
\setcopyright{rightsretained}
\acmDOI{10.475/123_4}
\acmISBN{123-4567-24-567/08/06}
\acmConference[NSPW '17]{New Security Paradigms Workshop}{October 2017}{Islamorada, Florida, USA}
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}
\usepackage{balance}
\date{\today}
\title{Is the Future of Authenticity All In Our Heads?}
\hypersetup{
 pdfauthor={},
 pdftitle={Is the Future of Authenticity All In Our Heads?},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.1.1 (Org mode 9.0.9)}, 
 pdflang={English}}
\begin{document}

\maketitle
\subtitle{Moving Passthoughts From the Lab to the World}

\section{Introduction}
\label{sec:org7565b18}

@@

\section{Background}
\label{sec:orgd1c0bca}

@@

\subsection{One-step, multi-factor authentication}
\label{sec:orgd374263}

@@

\subsection{Passthought authentication}
\label{sec:org5f238b7}

@@

\subsection{Passthoughts using in-ear EEG}
\label{sec:orga02de6f}

@@

\section{User attitudes and perceptions}
\label{sec:orgb81193b}

@@

\subsection{Contending with mind-reading machines}
\label{sec:org130081b}

@@

\subsection{What (do you think) EEG can reveal about a person?}
\label{sec:org9bcbfb5}

@@

This quote highlights how individuals' life experiences
might shape the way they engage (or refuse to engage) with brain-sensing devices.
In general, this quote and others motivate the need for a rich, qualitative understanding of people's first-hand experiences with brainscanning devices,
as well as data collection,
in order to understand what role BCI applications such as passthoughts could play in day-to-day life.
\section{Diversity and security of passthoughts}
\label{sec:orgbdf0190}

@@

\section{Two studies on passthoughts}
\label{sec:orgfbef5df}

@@

\subsection{A real-time passthought authenticator}
\label{sec:org3eefee0}

@@

\subsubsection{Study protocol}
\label{sec:orgc11cda4}

@@

\subsubsection{The effect of feedback}
\label{sec:org4733f32}

@@

\subsubsection{Exploring continuous re-calibration}
\label{sec:org75a13f2}

@@

\subsection{A longitudinal study on brainwave monitoring}
\label{sec:orge945d47}

@@

\subsubsection{Study protocol}
\label{sec:orgaef58fa}

@@

\subsubsection{A more diverse corpus}
\label{sec:org9537f53}

@@

\subsubsection{The space of possible passthoughts}
\label{sec:org8c9c160}
In another potentially fruitful analysis, such a corpus will allow us to perform statistical analysis of how passthoughts are drawn from the overall distribution of EEG signals. 
Using multi-dimensional clustering algorithms such as t-SNE \cite{VanDerMaaten2008} 
could assist us in understanding how particular passthoughts relate to other EEG signals that an individual expresses involuntarily throughout the day. 
These clusters will help us understand how likely or unlikely we are to observe a given passthought in context of a particular person's neural signals
Such analysis between subjects could help shed light how given passthoughts are expressed uniquely between individuals.

@@

\subsubsection{Usability and attitudes}
\label{sec:org23ec747}

@@

\subsubsection{Limitations}
\label{sec:orgccd84d5}

@@

\section{Privacy, Security: Choices, Tradeoffs}
\label{sec:org0d77b88}

@@

\subsection{Privacy}
\label{sec:org4fc7610}
As of yet, it is still not well understood what EEG signals might reveal about a person.
EEG signals that are not anonymized could come to be seen as private in the face of new methods of analysis.
(If your brainwaves can authenticate you, could they also uniquely identify you, even if your name is redacted?)
Differential privacy \cite{Dwork2014} presents one approach to dealing with the risk of privacy breaches with EEG signals.
By adding noise to datasets, differentially private databases can make strong guarantees about the likelihood of a de-anonymization attack on particular database queries.

\subsection{Security}
\label{sec:org930a1cf}
Device security presents another risk to passthought authentication.
Since EEG devices will transmit data, likely wirelessly \cite{Mihajlovic2015}, their data may be intercepted, depending on the security properties of the underlying transit protocol. 
When transferring authentication credentials in passthoughts, the ability to snoop on authentication attempts could present a dangerous attack vector.

@@

\subsection{Tradeoffs between security and privacy}
\label{sec:orgb3b49f5}

@@

\section{Further Future Directions}
\label{sec:org00ee623}

@@

\subsection{Continuous authentication}
\label{sec:orgcd9a59d}

@@

\subsection{Organic passwords}
\label{sec:orgc35e593}

If EEG signals are nonstationary (changing over time), passthoughts will require continuous re-calibration to maintain decent accuracy \cite{Vidaurre2006a}.
This feature of BCIs could have an unexpected benefit to security. 
If an individual's expression of their passthought in EEG is always changing, 
passthoughts themselves are effectively evergreen, automatically replaced or updated by nature of the authentication paradigm.
This feature could improve security, as an attacker able to compromise a passthought's EEG signature may not be able to log into the system in a few weeks time,
unless they are able to realistically mutate the signal over authentication attempts.
This feature of EEG also gives passthoughts a possible advantage over other methods for behavioral authentication, such as voice or keystroke dynamics \cite{Monrose1997}, which may change more slowly for individuals, if they change at all.
Future work should investigate this claim, perhaps using a longitudinal corpus such as the one described above.
\subsection{Authentication and the self}
\label{sec:org7caebfa}

@@

Such a scenario raises serious ethical, legal, and even philosophical questions. 
How does such a system conform to accepted definitions of a ``person''?
Who is a person to make decisions for their future self?
What are possible vectors for abuse?
In any case, this property of an authentication is, as far as we are aware, novel, 
and should be considered as we learn more about the strengths, weaknesses, and particular affordances of this developing method for authentication.
\subsection{Passthoughts by any other sensor?}
\label{sec:org5a6eb5e}

@@

\subsection{Health, neuroscience and BCIs}
\label{sec:org4d2b694}

@@

\section{Conclusion}
\label{sec:org07455b3}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{refs}
\balance
\end{document}
